---
title: "Canopy Cover and Death Model Research"
author: "Mitzi Zitler"
date: "4/16/2018"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(readr)
library(readxl)
```

If you have any interesting research about a particular tree species - either for canopy cover or death model purposes, this would be a good place for that!

```{r}
sort(species_tree$Common, decreasing = F)

species_tree <- street_trees %>%
  select(Species, Scientific, Family, Genus, Common) %>%
  unique() %>%
  print()
```

We need a canopy estimate for each species

#### alder: AL
```{r}
species_tree %>%
  filter(Common == "alder") %>%
  print()
```

#### Amur maackia:
```{r}
species_tree %>%
  filter(Common == "Amur maackia") %>%
  print()
```

#### apple:
```{r}
species_tree %>%
  filter(Common == "apple") %>%
  print()
```

#### aborvitae:
```{r}
species_tree %>%
  filter(Common == "aborvitae") %>%
  print()
```

#### ash:
```{r}
species_tree %>%
  filter(Common == "ash") %>%
  print()
```

#### azara:
```{r}
species_tree %>%
  filter(Common == "azara") %>%
  print()
```

#### baldcypress:
```{r}
species_tree %>%
  filter(Common == "baldcypress") %>%
  print()
```

#### bay laurel:
```{r}
species_tree %>%
  filter(Common == "bay laurel") %>%
  print()
```

#### beech:
```{r}
species_tree %>%
  filter(Common == "beech") %>%
  print()
```

#### birch:
```{r}
species_tree %>%
  filter(Common == "birch") %>%
  print()
```

#### black locust:
```{r}
species_tree %>%
  filter(Common == "black locust") %>%
  print()
```

#### boxelder:
```{r}
species_tree %>%
  filter(Common == "boxelder") %>%
  print()
```

#### cascara:
```{r}
species_tree %>%
  filter(Common == "cascara") %>%
  print()
```

#### catalpa:
```{r}
species_tree %>%
  filter(Common == "catalpa") %>%
  print()
```

#### cedar:
```{r}
species_tree %>%
  filter(Common == "cedar") %>%
  print()
```

#### chaste tree:
```{r}
species_tree %>%
  filter(Common == "chaste tree") %>%
  print()
```

#### cherry:
```{r}
species_tree %>%
  filter(Common == "cherry") %>%
  print()
```

#### chestnut:
```{r}
species_tree %>%
  filter(Common == "chestnut") %>%
  print()
```

#### Chinese pistache:
```{r}
species_tree %>%
  filter(Common == "Chinese pistache") %>%
  print()
```

#### Chinese toon:
```{r}
species_tree %>%
  filter(Common == "Chinese toon") %>%
  print()
```

#### chitalpa:
```{r}
species_tree %>%
  filter(Common == "chitalpa") %>%
  print()
```

#### crabapple:
```{r}
species_tree %>%
  filter(Common == "crabapple") %>%
  print()
```

#### crape myrtle:
```{r}
species_tree %>%
  filter(Common == "crape myrtle") %>%
  print()
```

#### cryptomeria:
```{r}
species_tree %>%
  filter(Common == "cryptomeria") %>%
  print()
```

#### cypress:
```{r}
species_tree %>%
  filter(Common == "cypress") %>%
  print()
```

#### dawn redwood:
```{r}
species_tree %>%
  filter(Common == "dawn redwood") %>%
  print()
```

#### dogwood:
```{r}
species_tree %>%
  filter(Common == "dogwood") %>%
  print()
```

#### Douglas-fir:
```{r}
species_tree %>%
  filter(Common == "Douglas-fir") %>%
  print()
```

#### dove tree:
```{r}
species_tree %>%
  filter(Common == "dove tree") %>%
  print()
```

#### elkhorn cedar:
```{r}
species_tree %>%
  filter(Common == "elkhorn cedar") %>%
  print()
```

#### elm:
```{r}
species_tree %>%
  filter(Common == "elm") %>%
  print()
```

#### empress tree:
```{r}
species_tree %>%
  filter(Common == "empress tree") %>%
  print()
```

#### eucalptus:
```{r}
species_tree %>%
  filter(Common == "eucalptus") %>%
  print()
```

#### euptelea:
```{r}
species_tree %>%
  filter(Common == "euptelea") %>%
  print()
```

#### false cypress:
```{r}
species_tree %>%
  filter(Common == "false cypress") %>%
  print()
```

#### fig:
```{r}
species_tree %>%
  filter(Common == "fig") %>%
  print()
```

#### fir:
```{r}
species_tree %>%
  filter(Common == "fir") %>%
  print()
```

#### fragrant epaulette tree:
```{r}
species_tree %>%
  filter(Common == "fragrant epaulette tree") %>%
  print()
```

#### franklinia:
```{r}
species_tree %>%
  filter(Common == "franklinia") %>%
  print()
```

#### fringe tree:
```{r}
species_tree %>%
  filter(Common == "fringe tree") %>%
  print()
```

#### giant sequoia:
```{r}
species_tree %>%
  filter(Common == "giant sequoia") %>%
  print()
```

#### ginkgo:
```{r}
species_tree %>%
  filter(Common == "ginkgo") %>%
  print()
```

#### glorybower:
```{r}
species_tree %>%
  filter(Common == "glorybower") %>%
  print()
```

#### golden chain tree:
```{r}
species_tree %>%
  filter(Common == "golden chain tree") %>%
  print()
```

#### golden rain tree:
```{r}
species_tree %>%
  filter(Common == "golden rain tree") %>%
  print()
```

#### hackberry:
```{r}
species_tree %>%
  filter(Common == "hackberry") %>%
  print()
```

#### hardy rubber tree:
```{r}
species_tree %>%
  filter(Common == "hardy rubber tree") %>%
  print()
```

#### hawthorn:
```{r}
species_tree %>%
  filter(Common == "hawthorn") %>%
  print()
```

#### hazelnut:
```{r}
species_tree %>%
  filter(Common == "hazelnut") %>%
  print()
```

#### hemlock:
```{r}
species_tree %>%
  filter(Common == "hemlock") %>%
  print()
```

#### holly:
```{r}
species_tree %>%
  filter(Common == "holly") %>%
  print()
```

#### honey locust:
```{r}
species_tree %>%
  filter(Common == "honey locust") %>%
  print()
```

#### hophornbeam:
```{r}
species_tree %>%
  filter(Common == "hophornbeam") %>%
  print()
```

#### hornbeam:
```{r}
species_tree %>%
  filter(Common == "hornbeam") %>%
  print()
```

#### horsechestnut:
```{r}
species_tree %>%
  filter(Common == "horsechestnut") %>%
  print()
```

#### incense cedar:
```{r}
species_tree %>%
  filter(Common == "incense cedar") %>%
  print()
```

#### Japanese raisin tree:
```{r}
species_tree %>%
  filter(Common == "Japanese raisin tree") %>%
  print()
```

#### juniper:
```{r}
species_tree %>%
  filter(Common == "juniper") %>%
  print()
```

#### katsura:
```{r}
species_tree %>%
  filter(Common == "katsura") %>%
  print()
```

#### Kentucky coffeetree:
```{r}
species_tree %>%
  filter(Common == "Kentucky coffeetree") %>%
  print()
```

#### larch:
```{r}
species_tree %>%
  filter(Common == "larch") %>%
  print()
```

#### lilac tree:
```{r}
species_tree %>%
  filter(Common == "lilac tree") %>%
  print()
```

#### linden:
```{r}
species_tree %>%
  filter(Common == "linden") %>%
  print()
```

#### madrone:
```{r}
species_tree %>%
  filter(Common == "madrone") %>%
  print()
```

#### magnolia, deciduous:
```{r}
species_tree %>%
  filter(Common == "magnolia, deciduous") %>%
  print()
```

#### magnolia, evergreen:
```{r}
species_tree %>%
  filter(Common == "magnolia, evergreen") %>%
  print()
```

#### maple, bigleaf:
```{r}
species_tree %>%
  filter(Common == "maple, bigleaf") %>%
  print()
```

#### maple, Japanese:
```{r}
species_tree %>%
  filter(Common == "maple, Japanese") %>%
  print()
```

#### maple, Norway:
```{r}
species_tree %>%
  filter(Common == "maple, Norway") %>%
  print()
```

#### maple, other:
```{r}
species_tree %>%
  filter(Common == "maple, other") %>%
  print()
```

#### maple, paperbark:
```{r}
species_tree %>%
  filter(Common == "maple, paperbark") %>%
  print()
```

#### maple, red:
```{r}
species_tree %>%
  filter(Common == "maple, red") %>%
  print()
```

#### maple, silver:
```{r}
species_tree %>%
  filter(Common == "maple, silver") %>%
  print()
```

#### medlar:
```{r}
species_tree %>%
  filter(Common == "medlar") %>%
  print()
```

#### melliodendron:
```{r}
species_tree %>%
  filter(Common == "melliodendron") %>%
  print()
```

#### mimosa tree:
```{r}
species_tree %>%
  filter(Common == "mimosa tree") %>%
  print()
```

#### monkey puzzle:
```{r}
species_tree %>%
  filter(Common == "monkey puzzle") %>%
  print()
```

#### mountain-ash:
```{r}
species_tree %>%
  filter(Common == "mountain-ash") %>%
  print()
```

#### mulberry:
```{r}
species_tree %>%
  filter(Common == "mulberry") %>%
  print()
```

#### myrtlewood:
```{r}
species_tree %>%
  filter(Common == "myrtlewood") %>%
  print()
```

#### ninebark:
```{r}
species_tree %>%
  filter(Common == "ninebark") %>%
  print()
```

#### oak, deciduous:
```{r}
species_tree %>%
  filter(Common == "oak, deciduous") %>%
  print()
```

#### oak, evergreen:
```{r}
species_tree %>%
  filter(Common == "oak, evergreen") %>%
  print()
```

#### oleaster:
```{r}
species_tree %>%
  filter(Common == "oleaster") %>%
  print()
```

#### olive:
```{r}
species_tree %>%
  filter(Common == "olive") %>%
  print()
```

#### osage orange:
```{r}
species_tree %>%
  filter(Common == "osage orange") %>%
  print()
```

#### pagoda tree:
```{r}
species_tree %>%
  filter(Common == "pagoda tree") %>%
  print()
```

#### palm:
```{r}
species_tree %>%
  filter(Common == "palm") %>%
  print()
```

#### paw paw:
```{r}
species_tree %>%
  filter(Common == "paw paw") %>%
  print()
```

#### peach:
```{r}
species_tree %>%
  filter(Common == "peach") %>%
  print()
```

#### pear:
```{r}
species_tree %>%
  filter(Common == "pear") %>%
  print()
```

#### Persian ironwood:
```{r}
species_tree %>%
  filter(Common == "Persian ironwood") %>%
  print()
```

#### persimmon:
```{r}
species_tree %>%
  filter(Common == "persimmon") %>%
  print()
```

#### pine:
```{r}
species_tree %>%
  filter(Common == "pine") %>%
  print()
```

#### planetree:
```{r}
species_tree %>%
  filter(Common == "planetree") %>%
  print()
```

#### plum:
```{r}
species_tree %>%
  filter(Common == "plum") %>%
  print()
```

#### poplar:
```{r}
species_tree %>%
  filter(Common == "poplar") %>%
  print()
```

#### Prunus, other:
```{r}
species_tree %>%
  filter(Common == "Prunus, other") %>%
  print()
```

#### quince:
```{r}
species_tree %>%
  filter(Common == "quince") %>%
  print()
```

#### rosebud:
```{r}
species_tree %>%
  filter(Common == "rosebud") %>%
  print()
```

#### redwood:
```{r}
species_tree %>%
  filter(Common == "redwood") %>%
  print()
```

#### rose of Sharon:
```{r}
species_tree %>%
  filter(Common == "rose of Sharon") %>%
  print()
```

#### sassafras:
```{r}
species_tree %>%
  filter(Common == "sassafras") %>%
  print()
```

#### serviceberry:
```{r}
species_tree %>%
  filter(Common == "serviceberry") %>%
  print()
```

#### seven son flower:
```{r}
species_tree %>%
  filter(Common == "seven son flower") %>%
  print()
```

#### silverbell:
```{r}
species_tree %>%
  filter(Common == "silverbell") %>%
  print()
```

#### smoketree:
```{r}
species_tree %>%
  filter(Common == "smoketree") %>%
  print()
```

#### snowbell:
```{r}
species_tree %>%
  filter(Common == "snowbell") %>%
  print()
```

#### sourwood:
```{r}
species_tree %>%
  filter(Common == "sourwood") %>%
  print()
```

#### spindle tree:
```{r}
species_tree %>%
  filter(Common == "spindle tree") %>%
  print()
```

#### spruce:
```{r}
species_tree %>%
  filter(Common == "spruce") %>%
  print()
```

#### stewartia:
```{r}
species_tree %>%
  filter(Common == "stewartia") %>%
  print()
```

#### strawberry tree:
```{r}
species_tree %>%
  filter(Common == "strawberry tree") %>%
  print()
```

#### sumac:
```{r}
species_tree %>%
  filter(Common == "sumac") %>%
  print()
```

#### sweetgum:
```{r}
species_tree %>%
  filter(Common == "sweetgum") %>%
  print()
```

#### tree-of-heaven:
```{r}
species_tree %>%
  filter(Common == "tree-of-heaven") %>%
  print()
```

#### tulip poplar:
```{r}
species_tree %>%
  filter(Common == "tulip poplar") %>%
  print()
```

#### tupelo:
```{r}
species_tree %>%
  filter(Common == "tupelo") %>%
  print()
```

#### unknown:
```{r}
species_tree %>%
  filter(Common == "unknown") %>%
  print()
```

#### walnut:
```{r}
species_tree %>%
  filter(Common == "walnut") %>%
  print()
```

#### Western redcedar:
```{r}
species_tree %>%
  filter(Common == "Western redcedar") %>%
  print()
```

#### willow:
```{r}
species_tree %>%
  filter(Common == "willow") %>%
  print()
```

#### wingnut:
```{r}
species_tree %>%
  filter(Common == "wingnut") %>%
  print()
```

#### witch hazel:
```{r}
species_tree %>%
  filter(Common == "witch hazel") %>%
  print()
```

#### yellow wood:
```{r}
species_tree %>%
  filter(Common == "yellow wood") %>%
  print()
```

#### yew:
```{r}
species_tree %>%
  filter(Common == "yew") %>%
  print()
```

#### zelkova:
```{r}
species_tree %>%
  filter(Common == "zelkova") %>%
  print()
```
